Our Title

### 2015-05-08 draft.tex
Added in Julie's "potential targets" section.

>>>>

Because of ISIL's ideology and need to maintain territory (as outlined above), if ISIL were to obtain a nuclear device, it is more likely that ISIL will select targets in its immediate vicinity rather than attempt an attack on the U.S. homeland. However, with that being said, the U.S. has many allies and interests in the region, and must therefore still work to counter the possibility that ISIL will obtain a nuclear device. Additionally, it is possible that ISIL will obtain a nuclear device solely to use as a threat or deterrent. The panic that would occur if ISIL obtained a nuclear device cannot be overstated, and merely having a device can help further ISIL's objectives.
